Dealing with Consumer Uncertainty: Online Product Reviews and What makes them helpful?

### 2022-09-22 Paper.Rmd
started discussion

@korfiatis2012 found that neutral rated reviews (3 out of 5 stars) imply indifference to readers. This means that prior information of the potential buyer can't be influenced by these neutral reviews and likely to be found less helpful compared to extreme reviews (1 or 5 stars) [@wang2018; @liu2014; @cao2011; @ghose2006]. As the reviews get more extremely rated they might strengthen or sway prior information that a potential consumer has, making them more helpful. This extremeness has more objective nature for Search Goods since there are fewer ways to express pleasantness or unpleasantness for a particular product. For instance a bad design in a laptop might cause fans to make much more noise than they should normally do. This information along with a very low rating may signal there are some inherent problems with that particular product, making the feedback more helpful. On the other hand, for Experience Goods and in this specific case movies, opinions for a given product might be much more subjective. For example, a reviewer might find a movie "childish" and give it one star, the other might find the movie "light-hearted and colorful" and give 5 stars, making the helpfulness subjective and decreasing its usefulness. Furthermore, for experience goods, it was found that opposite extremes to a potential buyer's prior expectations aren't impactful on the decision making process [@hoch1989]. In other words, prior expectations play a bigger role in decision making process for experience goods. Therefore it is hypothesized that:

@@

A positive linear relationship between the logarithm of Review Length and Perceived Helpfulness was proposed with Hypothesis 2. A strong relationship between Review Length and Perceived Helpfulness is observed (0.404, p \< 0.001) for Search Goods. This effect is moderated by Review Extremity since the interaction effect is significant with a negative sign (-0.043, p \< 0.001). As review rating increases the responsiveness of the Perceived Helpfulness to Review Length decreases. This means that for positive extreme reviews relatively shorter texts are more helpful. Logarithmic form also proves that words in a review shows diminishing returns to helpfulness. Experience Goods somewhat deviates from the results of Search Goods. There is a weak positive relationship between Review Length and Perceived Helpfulness (0.021, p \< 0.01). However, this positive relationship quickly turns to negative for higher ratings because of the presence of the interaction term between Review Length and Review Extremity (-0.015, p \< 0.001). For lower ratings Hypothesis 2 is fully supported but as the Review Extremity increases this support weakens.

For both good types the interaction effects are significantly negative (-0.043, p \< 0.001 ; -0.015, p \< 0.001). This means that as Review Extremity increases longer reviews become less helpful, supporting the idea of people spending more time evaluating negative information because it takes more time to read a longer review. However, there are nuances too. For Search Goods, the effect of the Review Length is always positive whether or not Review Extremity is low or high. On the contrary, for Experience Goods, after some point of Review Extremity longer reviews become "unhelpful" because the sign of the Review Length turns to negative. In this case Hypothesis 3 is supported wholly for Search Goods and somewhat supported for Experience Goods.

@@

>>>>

@korfiatis2012 found that neutral rated reviews (3 out of 5 stars) imply indifference to readers. This means that prior information of the potential buyer can't be influenced by these neutral reviews and likely to be found less helpful compared to extreme reviews (1 or 5 stars) [@wang2018; @liu2014; @cao2011; @ghose2006]. As the reviews get more extremely rated they might strengthen or sway prior information that a potential consumer has, making them more helpful. This extremeness has more objective nature for Search Goods since there are fewer ways to express pleasantness or unpleasantness for a particular product. For instance a bad design in a laptop might cause fans to make much more noise than they should normally do. This information along with a very low rating may signal that there are some inherent problems with the particular product, making the feedback more helpful. On the other hand, for Experience Goods and in the specific case of movies, opinions for a given product might be much more subjective. For example, a reviewer might find a movie "childish" and give it one star, another reviewer might find the movie "light-hearted and colorful" and give 5 stars, making the helpfulness subjective and decreasing its usefulness. Furthermore, for experience goods, it was found that opposite extremes to a potential buyer's prior expectations aren't impactful on the decision making process [@hoch1989]. In other words, prior expectations play a bigger role in decision making process for experience goods. Therefore it is hypothesized that:

@@

A positive linear relationship between the logarithm of Review Length and Perceived Helpfulness was proposed with Hypothesis 2. A strong relationship between Review Length and Perceived Helpfulness is observed (0.404, p \< 0.001) for Search Goods. This effect is moderated by Review Extremity since the interaction effect is significant with a negative sign (-0.043, p \< 0.001). As review rating increases the responsiveness of the Perceived Helpfulness to Review Length decreases. This means that for positive extreme reviews relatively shorter texts are more helpful. Logarithmic form also proves that additional words in a review shows diminishing returns to helpfulness. Experience Goods somewhat deviates from the results of Search Goods. There is a weak positive relationship between Review Length and Perceived Helpfulness (0.021, p \< 0.01). However, this positive relationship quickly turns to negative for higher ratings because of the presence of the interaction term between Review Length and Review Extremity (-0.015, p \< 0.001). For lower ratings Hypothesis 2 is fully supported but as the Review Extremity increases this support weakens.

For both good types the interaction effects are significantly negative (-0.043, p \< 0.001 ; -0.015, p \< 0.001). This means that as Review Rating increases longer reviews become less helpful, supporting the idea of people spending more time evaluating negative information because it takes more time to read a longer review. However, there are nuances too. For Search Goods, the effect of the Review Length is always positive whether or not Review Rating is low or high. On the contrary, for Experience Goods, after some point of Review Rating longer reviews become "unhelpful" because the sign of the Review Length turns to negative. In this case Hypothesis 3 is supported wholly for Search Goods and somewhat supported for Experience Goods.

@@

The results show a clear contrast between the objective nature of search goods versus the subjective nature of experience goods which once again validates the notion of Search and Experience goods classification that was developed by @nelson1970. It shouldn't be ignored that this contrast is only relevant for the case of electronics versus movies since the available data only included these products. Electronics such as laptops or phones carry very strong search attributes whereas movies can be classified as "pure experience" goods which can be considered as a special case [@liu2014].

Negativity Bias Theorem and Prospect Theory had a strong support in the case of search goods. The regression results showed that the reviews which had low ratings and/or reviews which had more negative words in them were found to be more helpful on the average. Additionally, Perceived Helpfulness has a higher responsiveness to Review Length when a review has a low rating which means that people care more about negative cues than positive cues.

-   talk about positive sentiments and ratings and compare them

```{=html}
<!-- -->
```
-   mention the search goods as well.

One reason why the statistical results for search goods came out just as expected can be accredited to their objective features. Properties of electronics are easily evaluated prior purchase. This means that it is comparatively easier to collect information on search goods than experience goods. Other than online consumer reviews on an online retail website, a potential buyer has an arsenal of product reviews which are available on tech enthusiastic websites where electronics are reviewed by professionals. Furthermore, some channels on YouTube offer product reviews where the reviewer inspects the product in question on camera. Thus, the potential buyer can gather a great amount of information even before accessing to the online retailer's website.

-   talk about the limitations as we go
